Learning CNN filters from user-drawn image makers for coconut-tree image classification

### 2020-06-08 main.tex
Updates from Overleaf

Classification of tree species in aerial images has been actively investigated~\cite{fassnacht2016review}. In \cite{puttemans2018comparing, aparna2018cnn}, the authors present solutions to detect coconut trees based on convolutional neural network (CNN) models. Vargas-Muñoz et al.~\cite{8899005} propose an active learning approach to reduce human effort in annotating images of coconut trees. They divide the problem in two stages: a stage that produces candidate image patches and a stage in which a CNN identifies the candidate patches with a coconut tree. We propose a different way to produce this classifier.

Despite this success, methods based on deep learning require a lot of annotated images for training, and annotating this volume of data is quite costly. Even interactive methods require large training sets. If these methods depend on huge training sets, their application may not be feasible in areas where it is impossible, or the cost of gathering and annotating these data sets is prohibitive. Much of the user's interaction with methods based on deep learning occurs through the annotation of the training set, and the user does not have much influence on the training process.

>>>>

Classification of tree species in aerial images has been actively investigated~\cite{fassnacht2016review}. In \cite{puttemans2018comparing} and~\cite{aparna2018cnn}, the authors present automatic solutions to detect coconut trees based on convolutional neural network (CNN) models. Despite these recent advances, CNN models usually require considerable human effort in image annotation to create large training sets. Vargas-Muñoz et al.~\cite{8899005}  propose an active learning approach to reduce human effort in annotating images of coconut trees. They divide the problem in two stages: a stage that produces candidate image patches for having or not a coconut tree and a stage in which a CNN identifies the candidate patches with a coconut tree. We propose a different way to produce this classifier.

methods based on deep learning require a lot of annotated images for training, and annotating this volume of data is quite costly. Even interactive methods require large training sets. If these methods depend on huge training sets, their application may not be feasible in areas where it is impossible, or the cost of gathering and annotating these data sets is prohibitive. Much of the user's interaction with methods based on deep learning occurs through the annotation of the training set, and the user does not have much influence on the training process.
